Discovery of the first quadruple gravitationally lensed quasar candidate with Pan-STARRS

### 2017-06-13 manuscript.tex
fixed referee comments

In this letter we report the serendipitous discovery of a quad lensed quasar candidate from the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS1, hereafter PS1) released images. To our knowledge, if proven with spectroscopic observations, this would be the first gravitational lens discovered in the PS1 data. We model the system to provide evidence in support of its lensing nature, and we conclude with the necessity of obtaining spectroscopic confirmation. Due to its position, this is not possible until the end of the year.

The lensed quasar was discovered as part of a variability study of Active Galactic Nuclei selected based on Mid-Infrared characteristics \citep{sec01}, and data from the USNO Robotic Astrometric Telescope \citep{zac15}.

@@

The structure of the paper is as follows:
In Section 2 we infer relative astrometry, photometry and photometric redshifts. In Section 3 we fit a mass model to the system. Discussions, conclusions and future works are presented in Section 4. We assume a cosmological model with $\Omega_M = 0.274$, $\Omega_L = 0.726$, and $h$ = 0.71. All magnitudes are in the AB system.

@@

The simple modeling with a point spread function (PSF) constructed from stars in the PS1 field of view (FOV) left large residuals at the locations of the four objects, that were significant enough to affect the derived parameters. We suspect that this is due to spatial variation in the PSF across the PS1 FOV, and have therefore adopted a technique of fitting the system with an analytical PSF, which it is assumed will not change on the small scale represented by the system. We did this using Hostlens \citep{rus16}, a variant of glafic \citep{ogu10b} which uses $\chi^2$ minimization in order to fit point sources as well as S{\'e}rsic \citep{ser63} profiles convolved with an analytical PSF. The analytical PSF is comprised of two concentric Moffat \citep{mof69} profiles, each one with its own full-width half maximum, ellipticity, orientation, and shape parameter. The two profiles are also characterized by a relative flux of one to the other. We successfully modeled the four objects as point sources convolved with the PSF, therefore showing that they are point-like. Our strategy was to run Hostlens starting from 100 different positions in the parameter space, select the best of the resulting models, and further run 10 Markov Chain Monte Carlo (MCMC) chains using the MetropolisÐHastings algorithm around it. The chains consist of one million steps, with an acceptance rate of $\sim0.3$, and we removed the first 1/5 of these (the ``burn-in'' steps). We also checked that the chains have converged, using the method of \citet{gel95}. The MCMC-derived uncertainties between the various analytical parameters are shown in Fig.~\ref{mcmc_hostlens}, and generated using corner.py \citep{for16}. In order to quantify additional uncertainties inherent in our method due to the non-analytical nature of the ``true'' PSF, we ran 100 simulations where we add noise of similar properties to the real images, on top of the best-fit model. Here, we created the best-fit model by using a PSF constructed from nearby stars, and we ran Hostlens on each of the 100 simulations, using an analytical PSF. As a final estimate of our uncertainties, we used the maximum between the MCMC-derived uncertainties and those from the simulations. We were able to obtain much improved residuals in all bands, and we show these in Fig.~\ref{hostlens}.

@@

The system is also bright in the infrared, with the unresolved magnitudes being: 11.524$\pm$0.022, 10.434$\pm$0.020, 6.769$\pm$0.015, and 4.518$\pm$0.023 in the WISE bands $-$ W1, W2, W3 and W4, respectively. The WISE colors W1$-$W2$=$1.1 and W2$-$W3$=$3.7 match very well those of quasars for redshift below 3.5 \citep[e.g.][]{wu12}.

Finally, the system is very likely also a radio source. The NRAO VLA Sky Survey (NVSS) images show a source, 2MASX J01471020+4630433, with flux 12.6 mJy at 1.4 GHz. The listed position for this source is only $3\arcsec$ away from the center of the lens, which is comparable with NVSS astrometric errors \citep{con98}. We are currently in the process of further observing the system in the radio with the Very Large Baseline Array (VLBA). Radio data is useful for the study of lensed quasars, as it provides high-resolution imaging of the source, as well as fluxes not affected by microlensing and extinction.

@@

We fit the photometry measured in Section 2 for the point-like sources and the faint red galaxy using spectral energy distribution (SED) templates. The colors of the point-like images are very similar (Table~1), consistent with being multiple images of the same source. Due to their point-like morphology, we suspect these to be quasars, and have therefore fit them with quasar templates in order to check the quality of the fit and to infer photometric redshifts. Photometric redshifts of quasars are notoriously difficult to constrain, due to the relatively featureless continua \citep{ric09} and the variable equivalent widths of the broad emission lines. Redshift was measured using two separate methods:
\begin{itemize}
\item The method of \citet{wu10} presents quasar colors as a function of redshifts. This is based on Sloan Digital Sky survey (SDSS) colors. PS1 bands are similar but not identical to the SDSS bands and we used the corrections of \citet{fin16} to obtain magnitudes in the SDSS system. Following \citet{wu10}, we minimized ${\chi}^2$ to obtain redshifts for each of the point sources. We plot $\chi^2_{\nu}$ in Figure~\ref{redshift} for each quasar image, and also by fitting all sources together. We notice that the curves are quite consistent with each other, as expected from the similar colors of the sources. In the latter case we obtain the best fit at $z = 0.820^{+0.006}_{-0.007}$. We notice a second minimum at $z \sim2.6$. For both minima the $\chi^2_{\nu}$ is $\lesssim1$, indicative of a good fit. 
\item LePhare \citep{arn99,ilb06} method uses quasar templates. We obtain the best fit at a redshift of $\sim 2.6-2.8$ for all four point sources.  These results agree with the second peak of the method above. The $\chi^2$ is between 13 and 125 for 4 degrees of freedom (5 filters). We find poorer fits (larger $\chi^2$) when using stellar or galactic SED templates, providing further support that the sources are quasars. In particular, the best-fit galaxy templates correspond to starburst galaxies at low redshift $\lesssim0.1$. At such low redshifts the sources would likely be resolved, not point-like. 
\end{itemize}

@@

@@

@@

@@

Finally, we note that this system is very similar to the well-studied quad lens RX J1131-1231 \citep{slu03}, in terms of image separation and overall configuration. However, our system appears to have a larger source redshift and brighter images by about 2 magnitudes \citep{slu06}. \citet{slu08} also measure flux discrepancies for RX J1131-1231, and show that these flux discrepancies can be explained by microlensing.

@@

\bibitem[Agnello et al.(2015)]{agn15} Agnello A., et al., 2015, MNRAS, 454, 1260 
\bibitem[Arnouts et al.(1999)]{arn99} Arnouts S., Cristiani S., Moscardini L., Matarrese S., Lucchin F., Fontana A., Giallongo E., 1999, MNRAS, 310, 540

\bibitem[Bertin \& Arnouts(1996)]{ber96} Bertin, E., \& Arnouts, S.\ 1996, \aaps, 117, 393 
\bibitem[Bonvin et al.(2017)]{bon17} Bonvin V., et al., 2017, MNRAS, 465, 4914 
\bibitem[Brewer \& Lewis(2008)]{bre08} Brewer, B.~J., \& Lewis, G.~F.\ 2008, \mnras, 390, 39

@@

\bibitem[Dai et al.(2010)]{dai10} Dai X., Kochanek C.~S., Chartas G., Koz{\l}owski S., Morgan C.~W., Garmire G., Agol E., 2010, ApJ, 709, 278 
\bibitem[Ding et al.(2017)]{din17} Ding X., et al., 2017, preprint (arXiv:1703.02041)

\bibitem[Fadely \& Keeton(2012)]{fad12} Fadely R., Keeton C.~R., 2012, MNRAS, 419, 936 
\bibitem[Finch \& Zacharias(2016)]{fin01} Finch, C.~T., \& Zacharias, N.\ 2016, AAS/Division of Dynamical Astronomy Meeting, 47, 203.03 
\bibitem[Finkbeiner et al.(2016)]{fin16} Finkbeiner, D.~P., Schlafly, E.~F., Schlegel, D.~J., et al.\ 2016, \apj, 822, 66
\bibitem[Foreman-Mackey(2016)]{for16} Foreman-Mackey, D. 2016, The Journal of Open Source Software, 24, doi:10.21105/joss.00024

@@

\bibitem[Tonry \& Onaka(2008)]{ton09} Tonry J., Onaka P.\ 2009, in Ryan S., ed., 
Proceedings of the Advanced Maui Optical and Space Surveillance Technologies Conference.
The Maui Economic Development Board, Kihei, HI, p. E40
\bibitem[Treu(2010)]{tre10} Treu, T.\ 2010, \araa, 48, 87
\bibitem[Treu \& Marshall(2016)]{Tre16} Treu, T., \& Marshall, P.~J.\ 2016, \aapr, 24, 11

\bibitem[Walsh, Carswell, \& Weymann(1979)]{wal79} Walsh D., Carswell R.~F., Weymann R.~J., 1979, Natur, 279, 381 
\bibitem[Wu \& Jia(2010)]{wu10} Wu, X.-B., \& Jia, Z.\ 2010, \mnras, 406, 1583 
\bibitem[Wu et al.(2012)]{wu12} Wu, X.-B., Hao, G., Jia, Z., Zhang, Y., \& Peng, N.\ 2012, \aj, 144, 49

@@

\begin{deluxetable}{l|ccccc}
\tablecolumns{5}  
\tablewidth{0pt} 
\tabletypesize{\tiny}
\setlength{\tabcolsep}{0.05in}
\tablenum{1} %\\               
\tablecaption{Relative astrometry and photometry}   
\tablehead{
\colhead{Property} & \colhead{A} & \colhead{B} & \colhead{C} & \colhead{D} & \colhead{G}\\
}
\startdata

@@

\tablecomments{
The first four columns are the four quasar images and the fifth column is the lens.
The first five rows are magnitude measurements derived using Hostlens, corrected for extinction. 
The next two rows are the relative positions of each object relative to A. We assume a pixel scale of $0.256\arcsec$. $\Delta\alpha$ is positive towards west, and $\Delta\delta$ towards north.
%The following three rows are relative i magnitudes and relative positions in arcseconds averaged between the i and y bands. 
%The next row shows the photometric redshift estimates following \citet{wu10}.
The last row shows the model prediction for the relative magnitudes relative to image A, from the best-fit mass model.
}
\end{deluxetable}

\begin{figure}
\epsscale{1.1}
\plottwo{f1.eps}{f2.eps}
\caption{
PS1 images of the lens candidate showing the four quasar images (A-D) with the lensing galaxy position G marked with and x. Left: close-up color image using the $g$ (blue), $i$ (green) and $y$ (red) filters. Right: $y$-band image of a 2 $\arcmin$ region around the system. The bright star south-east of the lens is saturated in the other bands.}
\label{lens}
\end{figure}

>>>>

{\bf In this letter we report the serendipitous discovery of a quad lensed quasar candidate from the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS1, hereafter PS1) released images. The lensed quasar was discovered as part of a variability study of Active Galactic Nuclei selected based on Mid-Infrared characteristics \citep{sec01}, and data from the USNO Robotic Astrometric Telescope \citep[URAT;][]{zac15}. To our knowledge, if proven with spectroscopic observations, this would be the first gravitational lens discovered in the PS1 data. We note that this system is very similar to the well-studied quad lens RX J1131-1231 \citep{slu03}, in terms of image separation and overall configuration. We model the system to provide evidence in support of its lensing nature, and we conclude with the necessity of obtaining spectroscopic confirmation. Due to its position, from the ground this is not possible until the end of the year.}

@@

The structure of the paper is as follows:
In Section 2 we infer relative astrometry, photometry and photometric redshifts. In Section 3 we fit a mass model to the system. Discussions, conclusions and future works are presented in Section 4. We assume a cosmological model with $\Omega_M = 0.274$, $\Omega_L = 0.726$, and $h$ = 0.71. All magnitudes are in the AB system {\bf except for WISE, which are in the Vega system}.

@@

The simple modeling with a point spread function (PSF) constructed from stars in the PS1 field of view (FOV) left large residuals at the locations of the four objects, that were significant enough to affect the derived parameters. We suspect that this is due to spatial variation in the PSF across the PS1 FOV, and have therefore adopted a technique of fitting the system with an analytical PSF, which it is assumed will not change on the small scale represented by the system. We did this using Hostlens \citep{rus16}, a variant of glafic \citep{ogu10b} which uses $\chi^2$ minimization in order to fit point sources as well as S{\'e}rsic \citep{ser63} profiles convolved with an analytical PSF. The analytical PSF is comprised of two concentric Moffat \citep{mof69} profiles, each one with its own full-width half maximum, ellipticity, orientation, and shape parameter. The two profiles are also characterized by a relative flux of one to the other. We successfully modeled the four objects as point sources convolved with the PSF, therefore showing that they are point-like. Our strategy was to run Hostlens starting from 100 different positions in the parameter space, select the best of the resulting models, and further run 10 Markov Chain Monte Carlo (MCMC) chains using the Metropolis-Hastings algorithm around it. The chains consist of one million steps, with an acceptance rate of $\sim0.3$, and we removed the first 1/5 of these (the ``burn-in'' steps). We also checked that the chains have converged, using the method of \citet{gel95}. The MCMC-derived uncertainties between the various analytical parameters are shown in Fig.~\ref{mcmc_hostlens}, and generated using corner.py \citep{for16}. In order to quantify additional uncertainties inherent in our method due to the non-analytical nature of the ``true'' PSF, we ran 100 simulations where we add noise of similar properties to the real images, on top of the best-fit model. Here, we created the best-fit model by using a PSF constructed from nearby stars, and we ran Hostlens on each of the 100 simulations, using an analytical PSF. As a final estimate of our uncertainties, we used the maximum between the MCMC-derived uncertainties and those from the simulations. We were able to obtain much improved residuals in all bands, and we show these in Fig.~\ref{hostlens}.

@@

The system is also bright in the infrared, with the unresolved magnitudes being: 11.524$\pm$0.022, 10.434$\pm$0.020, 6.769$\pm$0.015, and 4.518$\pm$0.023 in the WISE bands $-$ W1, W2, W3 and W4, respectively. 
%%The WISE colors W1$-$W2$=$1.1 and W2$-$W3$=$3.7 match very well those of quasars for redshift below 3.5 \citep[e.g.][]{wu12}.

Finally, the system is very likely also a radio source. The NRAO VLA Sky Survey (NVSS) images show a source, 2MASX J01471020+4630433, with flux 12.6 mJy at 1.4 GHz. The listed position for this source is only $3\arcsec$ away from the center of the lens, which is comparable with NVSS astrometric errors \citep{con98}. We are currently in the process of further observing the system in the radio with the Very Large Array (VLA). Radio data is useful for the study of lensed quasars, as it provides high-resolution imaging of the source, as well as fluxes not affected by microlensing and extinction.

@@

We fit the photometry measured in Section 2 for the point-like sources and the faint red galaxy using spectral energy distribution (SED) templates. The colors of the point-like images are very similar (Table~1), consistent with being multiple images of the same source. Due to their point-like morphology, we suspect these to be quasars, and have therefore fit them with quasar templates in order to check the quality of the fit and to infer photometric redshifts. Photometric redshifts of quasars are notoriously difficult to constrain, due to the relatively featureless continua \citep{ric09} and the variable equivalent widths of the broad emission lines. Redshift was measured using two separate methods:
\begin{itemize}
\item The method of \citet{wu10} presents quasar colors as a function of redshifts. This is based on Sloan Digital Sky survey (SDSS) colors. PS1 bands are similar but not identical to the SDSS bands and we used the corrections of \citet{fin16} to obtain magnitudes in the SDSS system. Following \citet{wu10}, we minimized ${\chi}^2$ to obtain redshifts for each of the point sources. {\bf We only used three of the colors as the Y band from UKIRT is very different from the PS1 y band.} We plot $\chi^2_{\nu}$ in Figure~\ref{redshift} for each quasar image, and also by fitting all sources together. We notice that the curves are quite consistent with each other, as expected from the similar colors of the sources. In the latter case we obtain the best fit at $z = 0.820^{+0.006}_{-0.007}$. We notice a second minimum at $z \sim2.6$. {\bf The 
 $\chi^2_{\nu}$ for the minima is large, which could be due to the large spread seen in the colors of \citet{wu10}. Because of the poor fit we did not attempt to use any prior from a quasar luminosity function.}
\item LePhare \citep{arn99,ilb06} method uses quasar templates. We obtain the best fit at a redshift of $\sim 2.6-2.8$ for all four point sources.  These results agree with the second peak of the method above. The $\chi^2$ is between 13 and 125 for 4 degrees of freedom (5 filters). We find poorer fits (larger $\chi^2$) when using stellar or galactic SED templates, providing further support that the sources are quasars. In particular, the best-fit galaxy templates correspond to starburst galaxies at low redshift $\lesssim0.1$. At such low redshifts the sources would likely be resolved, not point-like. 
{\bf \item A combination of SDSS and WISE photometry provides good discriminators between high and low redshifts. \citet{pom15} uses he ratio between WISE W1 and W2 bands to the i band flux, high values are expected for quasars below z = 1. We added the fluxes for all four images in the i band and we obtain a total magnitude of 14.4. We obtain ratios W1/i = 14.4 and W2/i = 39.0, which both indicate a redshift z $>$ 2, and are not compatible with the low value of z = 0.8, which would require ratios of W1/i = 50 and W2/i = 120. We also used the diagnostics from \citet{wu12}. As seen in Fig.~13 in this paper, the colors z - W1 and W2 - W3 discriminate well between low and high redshift. We obtain z - W1 = 2.8 and W2 - W3 = 3.7, which both suggest a redshift larger than z = 2. Our low value of 0.8 would require z - W1 = 4.0 and W2 - W3 = 3.0.
}
\end{itemize}

@@

{\bf
\section{URAT VARIABILITY}

URAT1 was a U. S. Naval Observatory project designed to provide accurate astrometry in the northern hemisphere down to about 18 mag. A single filter centered at $\sim$~720 nm was used, which is almost as red as the PS1 i filter. Observations at the Flagstaff Station over more than 3 years provided more than 50 observations for a large number of objects. The gravitational lens was discovered as part of project to study the variability of a sample of AGN selected based on WISE colors \citep{sec01}. We now present the results of this study for our quad lens, keeping in mind that the system was not resolved by URAT. To characterize the variability we used a typical method used for quasars, the structure function V, as presented in \citet{van04}. It uses the magnitude  differences between different epochs of observation to estimate variability at different time intervals (time lag). \citet{van04} used the structure function to characterize the variability of a large sample of Sloan quasars. We note that their study is statistical in nature and therefore only provides general properties which we will use to try to discriminate between the two photometric redshifts we obtained in the previous section.

In order to improve the results, we performed relative photometry using nearby stars in the 12 to 14 magnitude range, and removing stars that show variability and also removing some poor quality observations. We used more than 50 stars and 36 epochs over a time interval longer than two years. We estimate errors using the nearby stars with similar magnitudes. We obtained V = 0.074 and an average time lag of 297 days. According to Fig.~ 16 of \citet{van04}, this V value matches quasars at about z = 2 and therefore our photometric value of z = 2.6 is a better match than the low value of z = 0.8, which would require a V value of 0.05. We also used the absolute magnitude dependence in Fig.~11 of \citet{van04}. We estimate absolute magnitudes for our quasar using the demagnified average of images A, B and C. Assuming a composite quasar spectrum we estimate that the i-band magnitudes range between -24.8  and -25.20 at redshift 0.8 and between -27.6 and -27.9 at redshift 2.6. Again we see that the V value matches better a high luminosity quasar, and therefore the higher redshift is preferred.

{\bf Based on the variability results and the combination of WISE and PS1 colors in the previous section, we estimate the quasars redshift at about z = 2.6, which is preferred over the option of a low redshift z = 0.8.}
}

%%The restframe time lag is 165 and 83 days for the assumed redshifts of 0.8 and 2.6, respectively. The restframe wavelength is 400 and 200 nm for the two cases. While Fig.~8 in \citet{van04} shows that for the I band a value of V = 0.073 matches a restframe timelag of about 30 days, the smaller value of 83 days corresponding to z = 2.6 provides a better match than the longer timelag of 165 days, which corresponds to V $>$ 0.1

@@

{\bf In order to check if the $izy$ magnitudes for the lensing galaxy are compatible with the redshift we used the luminosity prior from BPZ \citep{ben00} to estimate the redshift. The observed magnitudes for z=0.57 correspond to an absolute magnitude of about -23.0 to -23.5 in R. From the Faber-Jackson relation \citep{fab76} we obtain R $\sim$~-23.6 and therefore the measured magnitudes are compatible with the estimated redshift.}

@@

{\bf In the introduction we noted the similarity with RX J1131-1231,} however our system appears to have a larger source redshift and brighter images by about 2 magnitudes \citep{slu06}. \citet{slu08} also measure flux discrepancies for RX J1131-1231, and show that these flux discrepancies can be explained by microlensing.

@@

@@

\bibitem[Agnello et al.(2015)]{agn15} Agnello A., et al., 2015, MNRAS, 454, 1260 
\bibitem[Arnouts et al.(1999)]{arn99} Arnouts S., Cristiani S., Moscardini L., Matarrese S., Lucchin F., Fontana A., Giallongo E., 1999, MNRAS, 310, 540
\bibitem[Ben{\'{\i}}tez(2000)]{ben00} Ben{\'{\i}}tez, N.\ 2000, \apj, 536, 571 
\bibitem[Bertin \& Arnouts(1996)]{ber96} Bertin, E., \& Arnouts, S.\ 1996, \aaps, 117, 393 
\bibitem[Bonvin et al.(2017)]{bon17} Bonvin V., et al., 2017, MNRAS, 465, 4914 
\bibitem[Brewer \& Lewis(2008)]{bre08} Brewer, B.~J., \& Lewis, G.~F.\ 2008, \mnras, 390, 39

@@

\bibitem[Dai et al.(2010)]{dai10} Dai X., Kochanek C.~S., Chartas G., Koz{\l}owski S., Morgan C.~W., Garmire G., Agol E., 2010, ApJ, 709, 278 
\bibitem[Ding et al.(2017)]{din17} Ding X., et al., 2017, preprint (arXiv:1703.02041)
\bibitem[DiPompeo et al.(2015)]{pom15} DiPompeo, M.~A., Bovy, J., Myers, A.~D., \& Lang, D.\ 2015, \mnras, 452, 3124 
\bibitem[Faber \& Jackson(1976)]{fab76} Faber, S.~M., \& Jackson, R.~E.\ 1976, \apj, 204, 668 
\bibitem[Fadely \& Keeton(2012)]{fad12} Fadely R., Keeton C.~R., 2012, MNRAS, 419, 936 
\bibitem[Finch \& Zacharias(2016)]{fin01} Finch, C.~T., \& Zacharias, N.\ 2016, AAS/Division of Dynamical Astronomy Meeting, 47, 203.03 
\bibitem[Finkbeiner et al.(2016)]{fin16} Finkbeiner, D.~P., Schlafly, E.~F., Schlegel, D.~J., et al.\ 2016, \apj, 822, 66
\bibitem[Foreman-Mackey(2016)]{for16} Foreman-Mackey, D. 2016, The Journal of Open Source Software, 24, doi:10.21105/joss.00024

@@

\bibitem[Tonry \& Onaka(2008)]{ton09} Tonry J., Onaka P.\ 2009, in Ryan S., ed., 
Proceedings of the Advanced Maui Optical and Space Surveillance Technologies Conference.
The Maui Economic Development Board, Kihei, HI, p. E40
\bibitem[Treu(2010)]{tre10} Treu, T.\ 2010, \araa, 48, 87
\bibitem[Treu \& Marshall(2016)]{Tre16} Treu, T., \& Marshall, P.~J.\ 2016, \aapr, 24, 11 
\bibitem[Vanden Berk et al.(2004)]{van04} Vanden Berk, D.~E., Wilhite, B.~C., Kron, R.~G., et al.\ 2004, \apj, 601, 692 
\bibitem[Walsh, Carswell, \& Weymann(1979)]{wal79} Walsh D., Carswell R.~F., Weymann R.~J., 1979, Natur, 279, 381 
\bibitem[Wu \& Jia(2010)]{wu10} Wu, X.-B., \& Jia, Z.\ 2010, \mnras, 406, 1583 
\bibitem[Wu et al.(2012)]{wu12} Wu, X.-B., Hao, G., Jia, Z., Zhang, Y., \& Peng, N.\ 2012, \aj, 144, 49

@@

\begin{deluxetable}{l|ccccc}
\tablecolumns{5}  
\tablewidth{0pt} 
\tabletypesize{\tiny}
\setlength{\tabcolsep}{0.05in}
\tablenum{1} %\\               
\tablecaption{Relative astrometry and photometry}   
\tablehead{
\colhead{Property} & \colhead{A} & \colhead{B} & \colhead{C} & \colhead{D} & \colhead{G}\\
\colhead{} & \colhead{(S1)} & \colhead{(M2)} & \colhead{(M1)} & \colhead{(S2)} & \colhead{}\\
}
\startdata

@@

\tablecomments{
The first four columns are the four quasar images and the fifth column is the lens.
We also label the images according to the arrival time.
The first five rows are magnitude measurements derived using Hostlens, corrected for extinction. 
The next two rows are the relative positions of each object relative to A. We assume a pixel scale of $0.256\arcsec$. $\Delta\alpha$ is positive towards west, and $\Delta\delta$ towards north.
%The following three rows are relative i magnitudes and relative positions in arcseconds averaged between the i and y bands. 
%The next row shows the photometric redshift estimates following \citet{wu10}.
The last row shows the model prediction for the relative magnitudes relative to image A, from the best-fit mass model.
}
\end{deluxetable}

\begin{figure}
\epsscale{1.1}
\plottwo{f1.eps}{f2.eps}
\caption{
PS1 images of the lens candidate showing the four quasar images (A-D) with the lensing galaxy position G marked with and x. Left: close-up color image using the $g$ (blue), $i$ (green) and $y$ (red) filters. The Gaia position for component D (26.792307, 46.511273) is used as absolute astrometric reference position for this system. Right: $y$-band image of a 2 $\arcmin$ region around the system. The bright star south-east of the lens is saturated in the other bands.}
\label{lens}
\end{figure}
